Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-27 robdml.tex
tex

As shown in the last three columns of \cref{tab:desth}, almost all combinations
lead to model collapse as long as $H_\mathsf{D}$ is calculated from a Softhard,
Distance, or Hardest triplet.
%
Due to the small $E[H_\mathsf{D}-H_\mathsf{S}]$ in the combination of Distance
and Hardest triplets, the adversarial examples will be weak and the model does
collapse, but the robustness gain is negligible.

\todo{Rev}

@@

For cases in upper triangular of \cref{tab:desth}, $E[H_\mathsf{S}] \leqslant E[H_\mathsf{D}]$,
which means most triplets will be turned into adversarial example by HM
to increase the hardness.
%
Although most of such cases end up with model collapse, the preliminary 
result suggests that HM from random to semihard is effective in significantly
improve the robustness without model collapse, at an expected cost on the R@1
performance on benign examples.

>>>>

As shown in the last three columns of \cref{tab:desth}, almost all combinations
lead to model collapse as long as $H_\mathsf{D}$ is calculated from a Softhard,
Distance, or Hardest triplet.
%
Due to the small $E[H_\mathsf{D}-H_\mathsf{S}]$ in the combination of Distance
and Hardest triplets, the adversarial examples will be weak and the model does
collapse, but the robustness gain is negligible.
%
Although $E[H]$ of Softhard is less than that of Distance or Hardest,
some hard adversarial examples are still created due to its large
$\text{Var}[H]$, which still result in a slow collapse.

@@

For cases in the upper triangular of \cref{tab:desth} where $E[H_\mathsf{S}]
\leqslant E[H_\mathsf{D}]$, most given triplets will be turned adversarial with
an increased hardness.
%
Although most of such cases end up with model collapse, the preliminary result
suggests that $\text{HM}[\mathcal{R},\mathcal{M}]$ is still effective in
improving the robustness without model collapse, at an penalty on the R@1.

\todo{R}
